---
title: "Delegation as a Prosocial Act under Social Awareness:
Revisiting the Intrinsic Value of Decision Rights"
author: "Tomo OKADA, Masao NAGATSUKA, and Toshihiko NANBA"
output:
  html_document:
    highlight: pygments
    theme: cerulean
    df_print: paged
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    number_section: yes
    code_folding: hide
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

- This file reproduces the main results, figures, and appendix tables reported in the manuscript.

### Load required packages {-}
```{r, message=FALSE}
library(tidyverse)
library(zTree)
library(DT)
library(here)
library(fixest)
library(modelsummary)
library(readxl)
```

---

### Load the original data from Bartling et al. (2014) {-}

- The results differ slightly from those reported in the paper, possibly because the session on 121206 contains missing values.

```{r}
bfsdata <- read.csv(here("data", "Bartling_original", "Bartling_original.csv")) %>%
  filter(maecontrol == 0,
         type == "Principal")

datatable(
  bfsdata,
  extensions = "Scroller",
  options = list(
    deferRender = TRUE,
    scrollY = 200,
    scrollX = TRUE,
    scroller = TRUE
  )
)
```

---

### Function for processing experimental data {-}

```{r, message = FALSE}
bartling <- function(file_path) {
  
  data <- zTreeTables(file_path, ignore.errors = TRUE)
  
  #-----------------------------
  # Global data
  #-----------------------------
  data_global <- 
    data$globals %>% 
    filter(Treatment == 1) %>%
    rename_all(gsub, pattern = "+\\[", replacement = "_") %>% 
    rename_all(gsub, pattern = "]", replacement = "")
  
  #-----------------------------
  # Subject-level data
  #-----------------------------
  data_subjects <- data$subjects
  
  #-----------------------------
  # Questionnaire data
  #-----------------------------
  questionnaire <- 
    readxl::read_excel(here("data", "Quesstionnaire.xlsx")) %>%
    select(
      sessionid = session_id,
      subject,
      female,
      economics,
      q_gaze_next = q2_8,
      q_gaze_nearby = q2_9,
      q_gaze_experimenter = q2_10,
      q_analyzed_by_experimenter = q2_11
    ) %>%
    mutate(
      sessionid = as.character(sessionid),
      subject = as.numeric(subject)
    )
  
  #-----------------------------
  # Final profit
  #-----------------------------
  finalprofit <- 
    data_subjects %>% 
    filter(Treatment == max(Treatment)) %>%
    select(finalprofit = Profitm, subject = Subject)
  
  #-----------------------------
  # Loss gamble / IoC
  #-----------------------------
  loss_ioc <- 
    data_subjects %>%
    filter(Treatment == 4) %>%
    transmute(
      subject = Subject,
      lossgamble = lossgamble,
      IoC = IoC
    ) %>%
    distinct()
  
  #-----------------------------
  # Part 1
  #-----------------------------
  data1 <- 
    data_subjects %>%
    filter(Treatment == 1) %>%
    rename_all(gsub, pattern = "+\\[", replacement = "_") %>% 
    rename_all(gsub, pattern = "]", replacement = "") %>%
    mutate(
      showupfee = 1200,
      type = ifelse(Type == 1, "Principal", "Agent")
    ) %>%
    relocate(Treatment, subject = Subject, sessionid = Date, showupfee, type) %>%
    {
      if ("Group_1" %in% names(.)) select(., !Group_1:ncol(.)) else .
    } %>%
    select(!Period:slow) %>%
    inner_join(finalprofit, by = "subject")
  
  #-----------------------------
  # Reshape Part 1 into tidy format
  #-----------------------------
  data1 <- data1 %>%
    pivot_longer(
      !c(subject, sessionid, finalprofit, showupfee, type, Treatment),
      names_to = c(".value", "situation"),
      names_sep = "_"
    ) %>% 
    mutate(
      period_game = case_when(
        situation == 1 ~ data_global$O_1,
        situation == 2 ~ data_global$O_2,
        situation == 3 ~ data_global$O_3,
        situation == 4 ~ data_global$O_4,
        situation == 5 ~ data_global$O_5,
        situation == 6 ~ data_global$O_6,
        situation == 7 ~ data_global$O_7,
        situation == 8 ~ data_global$O_8,
        situation == 9 ~ data_global$O_9,
        situation == 10 ~ data_global$O_10
      ),
      va = case_when(
        situation == 1 ~ data_global$VA_1,
        situation == 2 ~ data_global$VA_2,
        situation == 3 ~ data_global$VA_3,
        situation == 4 ~ data_global$VA_4,
        situation == 5 ~ data_global$VA_5,
        situation == 6 ~ data_global$VA_6,
        situation == 7 ~ data_global$VA_7,
        situation == 8 ~ data_global$VA_8,
        situation == 9 ~ data_global$VA_9,
        situation == 10 ~ data_global$VA_10
      ),
      vb = case_when(
        situation == 1 ~ data_global$VB_1,
        situation == 2 ~ data_global$VB_2,
        situation == 3 ~ data_global$VB_3,
        situation == 4 ~ data_global$VB_4,
        situation == 5 ~ data_global$VB_5,
        situation == 6 ~ data_global$VB_6,
        situation == 7 ~ data_global$VB_7,
        situation == 8 ~ data_global$VB_8,
        situation == 9 ~ data_global$VB_9,
        situation == 10 ~ data_global$VB_10
      ),
      vc = case_when(
        situation == 1 ~ data_global$VC_1,
        situation == 2 ~ data_global$VC_2,
        situation == 3 ~ data_global$VC_3,
        situation == 4 ~ data_global$VC_4,
        situation == 5 ~ data_global$VC_5,
        situation == 6 ~ data_global$VC_6,
        situation == 7 ~ data_global$VC_7,
        situation == 8 ~ data_global$VC_8,
        situation == 9 ~ data_global$VC_9,
        situation == 10 ~ data_global$VC_10
      ),
      vd = case_when(
        situation == 1 ~ data_global$VD_1,
        situation == 2 ~ data_global$VD_2,
        situation == 3 ~ data_global$VD_3,
        situation == 4 ~ data_global$VD_4,
        situation == 5 ~ data_global$VD_5,
        situation == 6 ~ data_global$VD_6,
        situation == 7 ~ data_global$VD_7,
        situation == 8 ~ data_global$VD_8,
        situation == 9 ~ data_global$VD_9,
        situation == 10 ~ data_global$VD_10
      ),
      stakesize = ifelse(situation <= 5, "low",
                  ifelse(situation >= 6, "high", NA)),
      conflict = ifelse(situation == 1, "0.75(Low)",
                 ifelse(situation == 2, "0.75(Low)",
                 ifelse(situation == 3, "0.5(High)",
                 ifelse(situation == 4, "0.5(High)",
                 ifelse(situation == 5, "1(No)",
                 ifelse(situation == 6, "0.75(Low)",
                 ifelse(situation == 7, "0.75(Low)",
                 ifelse(situation == 8, "0.5(High)",
                 ifelse(situation == 9, "0.5(High)",
                 ifelse(situation == 10, "1(No)", NA)))))))))),
      cost = ifelse(type == "Principal", pcost, acost),
      situation = as.numeric(situation)
    ) %>%
    relocate(
      c(sessionid, subject, situation, 
        finalprofit, showupfee, type,
        period_game, aeffort, peffort,
        mae = MAE, varianta = VariantA, 
        variantp = VariantP)
    ) %>%
    select(!c(Treatment, acost, pcost))
  
  #-----------------------------
  # Part 2
  #-----------------------------
  data2 <- data_subjects %>%
    filter(Treatment == 2) %>%
    rename_all(gsub, pattern = "+\\[", replacement = "_") %>%
    rename_all(gsub, pattern = "]", replacement = "") %>%
    select(Subject, OL_1:offeraccept_20) %>%
    pivot_longer(
      -Subject,
      names_to = c(".value", "situation"),
      names_sep = "_"
    ) %>%
    mutate(situation = as.numeric(situation))
  
  data2_control_lottery <- 
    data2 %>%
    filter(situation <= 10) %>%
    mutate(period_lottery = OL, subject = Subject) %>%
    select(!c(OL, Subject))
  
  data2_delegation_lottery <- 
    data2 %>%
    filter(situation > 10) %>%
    mutate(situation = situation - 10) %>%
    select(
      period_lottery_del = OL, 
      offeracceptd = offeraccept,
      subject = Subject, 
      situation
    )
  
  data2 <- 
    inner_join(
      data2_control_lottery, 
      data2_delegation_lottery, 
      by = c("subject", "situation")
    ) %>%
    relocate(period_lottery, period_lottery_del, offeraccept, offeracceptd) %>%
    filter(offeraccept != 0 & offeraccept != 1)
  
  #-----------------------------
  # Merge Part 1 and Part 2
  #-----------------------------
  x <- 
    inner_join(data1, data2, by = c("subject", "situation")) %>%
    left_join(loss_ioc, by = "subject") %>%
    mutate(
      IV = ifelse(type == "Principal", offeracceptd - offeraccept, NA)
    ) %>%
    select(-j)
  
  #-----------------------------
  # Merge questionnaire data
  #-----------------------------
  x <- 
    x %>%
    mutate(
      sessionid = as.character(sessionid),
      subject = as.numeric(subject)
    ) %>%
    left_join(questionnaire, by = c("sessionid", "subject"))
  
  return(x)
}
```

---

### Load and prepare the experimental data {-}

```{r, include=FALSE}
T1 <- 
  rbind(
    bartling(here("data", "211129_0916.xls")), 
    bartling(here("data", "221024_0854.xls")), 
    bartling(here("data", "221125_0902.xls")), 
    bartling(here("data", "230117_0857.xls")), 
    bartling(here("data", "230224_0850.xls"))
  ) %>%
  mutate(treatment = 1, .before = 1)

T2 <- 
  rbind(
    bartling(here("data", "211126_1144.xls")),
    bartling(here("data", "221024_1245.xls")),
    bartling(here("data", "221125_1222.xls")),
    bartling(here("data", "230117_1153.xls"))
  ) %>%
  mutate(treatment = 2, .before = 1)

T3 <- 
  rbind(
    bartling(here("data", "211217_1030.xls")), 
    bartling(here("data", "221110_0846.xls")), 
    bartling(here("data", "221205_0923.xls")), 
    bartling(here("data", "230116_0854.xls"))
  ) %>%
  mutate(treatment = 3, .before = 1)

T4 <- 
  rbind(
    bartling(here("data", "211217_1213.xls")), 
    bartling(here("data", "221110_1229.xls")),
    bartling(here("data", "221205_1232.xls")), 
    bartling(here("data", "230116_1234.xls")),
    bartling(here("data", "230224_1226.xls"))
  ) %>%
  mutate(treatment = 4, .before = 1)

# Combined dataset including both principals and agents
tidy_data <- rbind(T1, T2, T3, T4)

# Dataset restricted to principals
data <- 
  tidy_data %>%
  filter(type == "Principal") %>%
  group_by(sessionid, subject) %>%
  mutate(participant = cur_group_id()) %>%
  ungroup()
```

**Treatment Description.**

- T1: Partitioned and unidentified counterpart  
- T2: No partition and unidentified counterpart  
- T3: Partitioned and identified counterpart  
- T4: No partition and identified counterpart  

--- 

**Participants: 324 subjects (3236 observations).**  
  
- T1: 42 pairs (419 observations; 1 observation dropped because offeraccept was 0 or 1)
- T2: 39 pairs (387 observations; 3 observations dropped because offeraccept was 0 or 1)
- T3: 42 pairs (420 observations)
- T4: 39 pairs (390 observations)

```{r}
data %>%
  group_by(treatment) %>%
  summarise(
    total_obs = n()
  )
```

---

- Display the dataset

```{r}
tidy_data %>%
  datatable(
    data =., 
    #filter = 'bottom',
    extensions = 'Scroller',
    options = list(
    deferRender = TRUE,
    scrollY = 200,
    scrollX = TRUE,
    scroller = TRUE
  ))

```

---

### Analysis{-}

#### 4.2 Intrinsic Value of Decision Rights (IV){-}

```{r}

# Function to create bar plots by treatment

treatment_bar <- 
  function (df, var, num1, num2) {
      x <- df %>%
            group_by(treatment) %>%
            ggplot(aes(x= treatment, 
                       y = {{ var }})) +
            coord_cartesian(ylim=c(num1, num2)) +
            stat_summary(geom = "col", fun = "mean", fill = "grey50", width = 0.5) +  
            stat_summary( fun.data = "mean_se", 
                          geom = "errorbar", 
                          width = .2, color = "grey20") +
            theme_bw() +
            labs(x = "Treatment") +
            theme(axis.title.y = element_blank())
      
      return(x)
  }


```


- Descriptive statistics of IV by treatment, including Bartling et al. (2014)

```{r}

# Combine IV data from our experiment with Bartling et al. (2014)

data_main <- data %>%
  select(IV, mae, peffort, treatment)

bfsdata_main <- bfsdata %>%
  select(IV, mae, peffort) %>%
  mutate(treatment = "Bartling et al. (2014)")

data_main_joined <- rbind(data_main, bfsdata_main) 

# Summary statistics by treatment
data_main_joined  %>%
  group_by(treatment) %>%
  summarise(
    mean_IV = mean(IV, na.rm = TRUE),
    sd_IV   = sd(IV, na.rm = TRUE),
    n       = sum(!is.na(IV)),
    se_IV   = sd_IV / sqrt(n)
  )
```

- Measured intrinsic value of decision rights (IV) by treatment (Figure 2)



```{r}
# Bar plot of IV by treatment (with standard error bars)

data %>%
  treatment_bar(., IV, 0, 45)

```

**Measured IV: T1 vs T4**

- We first compare the measured intrinsic value of decision rights (IV) between T1 and T4 using a two-sided Wilcoxon rank-sum test.
- The null hypothesis of equal distributions is rejected ($W = 95{,}606$, $p < 0.001$).  
- IV is significantly higher in T1 than in T4, consistent with H2P rather than H2R.

```{r}

# Extract observations for T1 and T4 only
df_T1T4 <- data %>%
  filter(treatment %in% c(1, 4)) %>%
  mutate(treatment = factor(treatment))

# Two-sided Wilcoxon rank-sum test
wilcox.test(
  IV ~ treatment,
  data = df_T1T4,
  exact = FALSE
)

```
  
**Regression analysis for measured IV**  

- We next estimate regression models for measured IV. 
- Columns (1) and (2) use treatment indicators with T1 as the reference category.
- Columns (3) and (4) decompose the treatment effects into the two treatment dimensions: openness (open) and counterpart identification (identified).
- Following Ferreira et al. (2020), Columns (2) and (4) additionally control for gender, a dummy for students in Economics or Management, and behavioral measures from the Loss Aversion and Illusion of Control tasks.

```{r}

# Define treatment dimensions: openness (no partition) and counterpart identification
data <- data %>%
  mutate(
    open = ifelse(treatment %in% c(2, 4), 1, 0),
    identified = ifelse(treatment %in% c(3, 4), 1, 0)
  )

# Treatment-based specifications
res_tr1 <- feols(
  IV ~ i(treatment, ref = 1),
  data = data,
  cluster = "participant"
)

res_tr2 <- feols(
  IV ~ i(treatment, ref = 1) + lossgamble + IoC + female + economics,
  data = data,
  cluster = "participant"
)

# Mechanism-based specifications
res_mech1 <- feols(
  IV ~ open * identified,
  data = data,
  cluster = ~participant
)

res_mech2 <- feols(
  IV ~ open * identified + lossgamble + IoC + female + economics,
  data = data,
  cluster = ~participant
)

# Regression table (displayed and exported)
modelsummary(
  list(
    "(1) Treatment" = res_tr1,
    "(2) Treatment" = res_tr2,
    "(3) Mechanism" = res_mech1,
    "(4) Mechanism" = res_mech2
  ),
  coef_rename = c(
    "treatment::2" = "T2",
    "treatment::3" = "T3",
    "treatment::4" = "T4",
    "lossgamble" = "Loss Aversion",
    "IoC" = "Illusion of Control",
    "female" = "Female",
    "economics" = "Economics & Management"
  ),
  coef_order = c(
    "treatment::2",
    "treatment::3",
    "treatment::4",
    "open",
    "identified",
    "open:identified",
    "lossgamble",
    "IoC",
    "female",
    "economics"
  ),
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = "({std.error})",
  gof_omit = "IC|Log|Adj"
)
```

**H3 test: positivity of IV in all treatments**

- Finally, we test Hypothesis 3 by examining whether the mean measured IV is significantly greater than zero in each treatment.
- We report the treatment-level mean IV, the raw p-value from a one-sample t-test against zero, and the Bonferroni-adjusted p-value.
- The mean IV is significantly positive in all treatments (all Bonferroni-adjusted $p < 0.001$), supporting H3.

```{r}
# H3 test: positivity of IV in all treatments
data %>%
  group_by(treatment) %>%
  summarise(
    mean_IV = mean(IV, na.rm = TRUE),
    p_raw = t.test(IV, mu = 0)$p.value
  ) %>%
  mutate(
    p_adj = p.adjust(p_raw, method = "bonferroni")
  )
```

--- 

#### 4.3 Delegation Threshold (<u>e</u>) {-}

- Descriptive statistics of minimum effort requirement (<u>e</u>) by treatment, including Bartling et al. (2014)

```{r}
# Summary statistics by treatment
data_main_joined  %>%
  group_by(treatment) %>%
  summarise(
    mean_mae = mean(mae, na.rm = TRUE),
    sd_mae   = sd(mae, na.rm = TRUE),
    n       = sum(!is.na(mae)),
    se_mae   = sd_mae / sqrt(n)
  )
```

- Minimum effort requirement (<u>e</u>) by treatment (Figure 3)

```{r}
# Bar plot of MAE by treatment (with standard error bars)
data %>%
  group_by(treatment) %>%
  treatment_bar(., mae, 45, 65) +
  theme_bw()

```


**Minimum effor requirement <u>e</u>: T1 vs T4**

- We next compare the minimum effort requirement (<u>e</u>) between T1 and T4 using a two-sided Wilcoxon rank-sum test. 
- The null hypothesis of equal distributions is rejected ($W = 97{,}040$, $p < 0.001$). 
- <u>e</u> is significantly higher in T1 than in T4, consistent with H2P rather than H2R.

```{r}
# Two-sided Wilcoxon rank-sum test
wilcox.test(
  mae ~ treatment,
  data = df_T1T4,
  exact = FALSE
)
```

**Regression analysis for minimum effort requirement (<u>e</u>)**

- We estimate regression models for the minimum effort requirement (<u>e</u>).  
- The set of explanatory variables is identical to that used in the IV regressions.

```{r}
# Treatment-based specifications
res_tr1 <- feols(
  mae ~ i(treatment, ref = 1),
  data = data,
  cluster = "participant"
)

res_tr2 <- feols(
  mae ~ i(treatment, ref = 1) + lossgamble + IoC + female + economics,
  data = data,
  cluster = "participant"
)

# Mechanism-based specifications
res_mech1 <- feols(
  mae ~ open * identified,
  data = data,
  cluster = ~participant
)

res_mech2 <- feols(
  mae ~ open * identified + lossgamble + IoC + female + economics,
  data = data,
  cluster = ~participant
)

# Regression table
modelsummary(
  list(
    "(1) Treatment" = res_tr1,
    "(2) Treatment" = res_tr2,
    "(3) Mechanism" = res_mech1,
    "(4) Mechanism" = res_mech2
  ),
  coef_rename = c(
    "treatment::2" = "T2",
    "treatment::3" = "T3",
    "treatment::4" = "T4",
    "lossgamble" = "Loss Aversion",
    "IoC" = "Illusion of Control",
    "female" = "Female",
    "economics" = "Economics & Management"
  ),
  coef_order = c(
    "treatment::2",
    "treatment::3",
    "treatment::4",
    "open",
    "identified",
    "open:identified",
    "lossgamble",
    "IoC",
    "female",
    "economics"
  ),
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = "({std.error})",
  gof_omit = "IC|Log|Adj"
)
```

---  


#### 4.4 Ruling Out Alternative Explanations {-}

- Descriptive statistics of principal/s effort level (E) by treatment, including Bartling et al. (2014)

```{r}
# Summary statistics by treatment
data_main_joined  %>%
  group_by(treatment) %>%
  summarise(
    mean_peffort = mean(peffort, na.rm = TRUE),
    sd_peffort   = sd(peffort, na.rm = TRUE),
    n       = sum(!is.na(peffort)),
    se_peffort   = sd_peffort / sqrt(n)
  )

```

- Principal's effort level (E) by treatment (Figure 4)

```{r}
# Bar plot of MAE by treatment (with standard error bars)

data %>%
  group_by(treatment) %>%
  treatment_bar(., peffort, 50, 70) +
  theme_bw()
```

**Regression analysis for principal's effort level (E)**

- We estimate regression models for principal's effort level (E)).  
- The set of explanatory variables is identical to that used in the IV regressions.

```{r}
# Treatment-based specifications
res_tr1 <- feols(
  peffort ~ i(treatment, ref = 1),
  data = data,
  cluster = "participant"
)

res_tr2 <- feols(
  peffort ~ i(treatment, ref = 1) + lossgamble + IoC + female + economics,
  data = data,
  cluster = "participant"
)


# Mechanism-based specifications
res_mech1<- feols(peffort ~ open * identified,
      data = data,
      cluster = ~participant)

res_mech2<- feols(peffort ~ open * identified + lossgamble + IoC + female + economics,
      data = data,
      cluster = ~participant)

# Regression table
modelsummary(
  list(
    "(1) Treatment" = res_tr1,
    "(2) Treatment" = res_tr2,
    "(3) Mechanism" = res_mech1,
    "(4) Mechanism" = res_mech2
  ),
  coef_rename = c(
    "treatment::2" = "T2",
    "treatment::3" = "T3",
    "treatment::4" = "T4",
    "lossgamble" = "Loss Aversion",
    "IoC" = "Illusion of Control",
    "female" = "Female",
    "economics" = "Economics & Management"
  ),
  coef_order = c(
    "treatment::2",
    "treatment::3",
    "treatment::4",
    "open",
    "identified",
    "open:identified",
    "lossgamble",
    "IoC"
  ),
  stars = c("*" = .1, "**" = .05, "***" = .01),
  statistic = "({std.error})",
  gof_omit = "IC|Log|Adj"
)
```

- The Wald test examines whether all treatment effects (T2–T4 relative to T1) are jointly equal to zero.  
- The null cannot be rejected ($p = 0.872$), indicating no overall treatment effect on effort relative to T1.
```{r}
wald(res_tr1, keep = "treatment")
```

---


### Appendix A: Self-reported awareness of others {-}

**Post-experimental questionnaire items (social awareness measures).**

- Q1: During the experiment, were you concerned about the presence or gaze of the participant sitting next to you?  
- Q2: During the experiment, were you concerned about the presence or gaze of other nearby participants, excluding the one sitting next to you?  
- Q3: During the experiment, were you concerned about the presence or gaze of the experiment staff?  
- Q4: During the experiment, were you concerned that the experimenters would later observe data on your behavior?  

---  

- Responses were recorded on a seven-point Likert scale, where 1 indicates “not at all concerned,” 4 indicates a neutral response, and 7 indicates “very concerned.”

- All statistics are based on responses from participants in the role of principals.

- The table reports treatment-level means of each item (with standard deviations in parentheses). The rightmost column reports p-values from ANOVA tests of equality across treatments.

```{r}
#--------------------------
# 1. Descriptive statistics
#--------------------------
# Compute means, standard deviations, and sample sizes by treatment

desc_stats <- data %>%
  group_by(treatment) %>%
  summarise(
    q_gaze_next_mean  = mean(q_gaze_next, na.rm = TRUE),
    q_gaze_next_sd    = sd(q_gaze_next, na.rm = TRUE),
    q_gaze_next_n     = sum(!is.na(q_gaze_next)),

    q_gaze_nearby_mean  = mean(q_gaze_nearby, na.rm = TRUE),
    q_gaze_nearby_sd    = sd(q_gaze_nearby, na.rm = TRUE),
    q_gaze_nearby_n     = sum(!is.na(q_gaze_nearby)),

    q_gaze_experimenter_mean = mean(q_gaze_experimenter, na.rm = TRUE),
    q_gaze_experimenter_sd   = sd(q_gaze_experimenter, na.rm = TRUE),
    q_gaze_experimenter_n    = sum(!is.na(q_gaze_experimenter)),

    q_analyzed_by_experimenter_mean = mean(q_analyzed_by_experimenter, na.rm = TRUE),
    q_analyzed_by_experimenter_sd   = sd(q_analyzed_by_experimenter, na.rm = TRUE),
    q_analyzed_by_experimenter_n    = sum(!is.na(q_analyzed_by_experimenter)),

    .groups = "drop"
  )

#--------------------------
# 2. ANOVA
#--------------------------
# Test whether treatment differences are statistically significant

anova_q_gaze_next <- summary(aov(q_gaze_next ~ factor(treatment), data = data))
anova_q_gaze_nearby <- summary(aov(q_gaze_nearby ~ factor(treatment), data = data))
anova_q_gaze_experimenter <- summary(aov(q_gaze_experimenter ~ factor(treatment), data = data))
anova_q_analyzed_by_experimenter <- summary(aov(q_analyzed_by_experimenter ~ factor(treatment), data = data))

# Extract p-values
p_q_gaze_next <- anova_q_gaze_next[[1]]["factor(treatment)", "Pr(>F)"]
p_q_gaze_nearby <- anova_q_gaze_nearby[[1]]["factor(treatment)", "Pr(>F)"]
p_q_gaze_experimenter <- anova_q_gaze_experimenter[[1]]["factor(treatment)", "Pr(>F)"]
p_q_analyzed_by_experimenter <- anova_q_analyzed_by_experimenter[[1]]["factor(treatment)", "Pr(>F)"]

#--------------------------
# 3. Appendix table: means
#--------------------------
# Prepare treatment-level means for each variable

appendix_means <- data %>%
  group_by(treatment) %>%
  summarise(
    q_gaze_next = mean(q_gaze_next, na.rm = TRUE),
    q_gaze_nearby = mean(q_gaze_nearby, na.rm = TRUE),
    q_gaze_experimenter = mean(q_gaze_experimenter, na.rm = TRUE),
    q_analyzed_by_experimenter = mean(q_analyzed_by_experimenter, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_longer(
    cols = c(q_gaze_next, q_gaze_nearby, q_gaze_experimenter, q_analyzed_by_experimenter),
    names_to = "variable",
    values_to = "mean"
  ) %>%
  mutate(treatment = paste0("T", treatment)) %>%
  pivot_wider(
    names_from = treatment,
    values_from = mean
  )

#--------------------------
# 4. Appendix table: standard deviations
#--------------------------
# Prepare treatment-level standard deviations

appendix_sds <- data %>%
  group_by(treatment) %>%
  summarise(
    q_gaze_next = sd(q_gaze_next, na.rm = TRUE),
    q_gaze_nearby = sd(q_gaze_nearby, na.rm = TRUE),
    q_gaze_experimenter = sd(q_gaze_experimenter, na.rm = TRUE),
    q_analyzed_by_experimenter = sd(q_analyzed_by_experimenter, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_longer(
    cols = c(q_gaze_next, q_gaze_nearby, q_gaze_experimenter, q_analyzed_by_experimenter),
    names_to = "variable",
    values_to = "sd"
  ) %>%
  mutate(treatment = paste0("T", treatment)) %>%
  pivot_wider(
    names_from = treatment,
    values_from = sd,
    names_prefix = "sd_"
  )

#--------------------------
# 5. Appendix table: p-values
#--------------------------
# Store ANOVA p-values

appendix_p <- data.frame(
  variable = c("q_gaze_next", "q_gaze_nearby", "q_gaze_experimenter", "q_analyzed_by_experimenter"),
  p_value = c(p_q_gaze_next, p_q_gaze_nearby, p_q_gaze_experimenter, p_q_analyzed_by_experimenter)
)

#--------------------------
# 6. Final appendix table
#--------------------------
# Combine means, standard deviations, and p-values

appendix_table <- appendix_means %>%
  left_join(appendix_sds, by = "variable") %>%
  left_join(appendix_p, by = "variable") %>%
  mutate(
    variable = recode(variable,
      "q_gaze_next" = "Q1",
      "q_gaze_nearby" = "Q2",
      "q_gaze_experimenter" = "Q3",
      "q_analyzed_by_experimenter" = "Q4"
    ),
    T1 = paste0(round(T1, 2), " (", round(sd_T1, 2), ")"),
    T2 = paste0(round(T2, 2), " (", round(sd_T2, 2), ")"),
    T3 = paste0(round(T3, 2), " (", round(sd_T3, 2), ")"),
    T4 = paste0(round(T4, 2), " (", round(sd_T4, 2), ")"),
    p_value = round(p_value, 3)
  ) %>%
  select(variable, T1, T2, T3, T4, p_value)

appendix_table
```



```{r}
sessionInfo()
```




